---
title: "RPisco_User_Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RPisco_User_Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

# **RPisco: tools for manipulate PISCO climatic databases of SENAMHI (Peru)**

The RPisco package contains tools for manipulating PISCO climatic databases from SENAMHI (Peru).

```{r}
library(RPisco)
```

**1. Installation**

Install RPisco from Github:
```	
> library(devtools)
> install_github("GeomarPerales/RPisco")		
```
**2. RPisco Package*

The RPisco package contains the following tools: extraction of daily/monthly PISCO data, processing PISCO data from daily/monthly series to annual series, and obtaining monthly/yearly averages from PISCO data.

**3. Precipitation - Precipitación**

- **3.1 Average Rainfall**

Daily data
```{r}
PISCO.file <- "D:\\PISCOd_pp_2.1.nc"
x <- data.frame(PISCO.file, -76.11, -13.11)
data <- piscod(x)
head(data) 
```

Monthly data
```{r}
PISCO.file <- "D:\\PISCOm_pp_2.1.nc"
x <- data.frame(PISCO.file, -76.11, -13.11)
data <- piscom(x)
head(data)
```

**4. Temperature - Temperatura**

- **4.1 Minimum Temperature - Temperatura mínima**

Daily data
```{r}
PISCO.file <- "D:\\PISCOd_tmn_v1.1.nc"
x <- data.frame(PISCO.file, -76.11, -13.11)
data <- piscod(x)
head(data)
```

Monthly data
```{r}
PISCO.file <- "D:\\PISCOm_tmn_v1.1.nc"
x <- data.frame(PISCO.file, -76.11, -13.11)
data <- piscom(x)
head(data)
```

- **4.2 Maximum Temperature**

Daily data
```{r}
PISCO.file <- "D:\\PISCOd_tmx_v1.1.nc"
x <- data.frame(PISCO.file, -76.11, -13.11)
data <- piscod(x)
head(data)
```

Monthly data
```{r}
PISCO.file <- "D:\\PISCOm_tmx_v1.1.nc"
x <- data.frame(PISCO.file, -76.11, -13.11)
data <- piscom(x)
head(data)
```


**6. References**

Aybar. (2017). Use of the gridded PISCO precipitation product in studies, research, and operational hydrometeorological monitoring and forecasting systems. Lima: SENAMHI.
